\bf Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid

### 2014-09-11 Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid/main.tex
Tuning

\section{Comparison Algorithm Parameter Tuning}
\label{sec-tuning}

~\cite{goldman:2012:ltga} % Bisection with no parameters

~\cite{goldman:2014:p3}

~\cite{jovanovic:1997:ruleofthree}

>>>>

\section{Comparison Algorithm Parameter Tuning}
\label{sec-tuning}
While four of the six algorithms in our experiments do not require any user specified parameters,
hBOA and LTGA both use a population size parameter. To ensure these techniques are not unfairly
handicapped, we have extensively tuned each algorithm to each problem size for each problem to
determine the optimal population size using the bisection method \citep{sastry:2001:bisection}.
Extended by \cite{goldman:2012:ltga} the bisection sets the population size by iteratively
doubling the population size until some success criteria is met and then performing bisection
between the lowest successful and highest unsuccessful sizes. Thus the minimum population size
which meets the success criteria is found. \cite{goldman:2014:p3} proposed a success criteria
of performing $r$ successful runs in a row, such that the expected failure rate can be bounded
above by $\frac{3}{r+1}$~\cite{jovanovic:1997:ruleofthree}. As P3 and the other three algorithms
do not prematurely converge, we chose $r=100$ to similarly ensure hBOA and LTGA almost never do.
